Sound Automated Synthesis of Digital Controllers

### 2016-10-12 paper/paper.tex
more fixes

Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial. Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
\begin{equation}
\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}.
\end{equation}

@@

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete-model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle;
\item the controller $\hat{C}(z)$ is a minimum-phase system. 
\end{itemize}
\end{mylemma}

@@

\begin{proof}
Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from $\nu(k+i)$ for every  integer $k\neq 0$. The autocorrelation function of $\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
\begin{equation}
R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu]=\sigma_{Q}^{2}\cdot \delta(\tau),
\end{equation}
where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.

>>>>

Let $\hat{C}(z)$ be the transfer function of the digital controller represented using this FWL with integer size $I$ and fractional
size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
%Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$ 
%domain, {\it i.e.} a Fixed-Point Finite Word Length with integer size $I$ and fractional
%size $F$, we shall denote this domain as $\mathbb{R}\langle I,F \rangle$ 
and assume that there exists a function $FWL[\cdot]:\mathbb{R}^{n}\rightarrow \mathbb{R}^{n}\langle I,F \rangle$, which applies the FWL effects to a polynomial. Thus the perturbed controller model $\hat{C}(z)$ may be computed from the original model $C(z)=\frac{N_{C}(z)}{D_{C}(z)}$ using the following expression:
\begin{equation}
\hat{C}(z)=\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}.
\end{equation}
In the case of a synthesised controller, because the synthesis is performed using FWL, $\hat{C}(z) \equiv C(z)$.

@@

\begin{mylemma}{\cite{Bessa16,fadali}}
\label{lemma:eq_int_stab}
A feedback hybrid control system as shown in Fig.~\ref{fig:sampledsystem}, with a FWL implementation of the digital controller $\hat{C}(z) = \frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}$ and uncertain discrete-model of the plant $\hat{G}(z)=G(z)+\Delta G_{P}(z)=\frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$, is BIBO-stable if and only if:
\begin{itemize}
\item  the roots of characteristic polynomial $S(z)$ are inside the open unit circle, where $S(z)$ is:
\begin{equation}
\label{eq:internal_stab_lemma}
S(z)=FWL[N_{C}(z)]\hat{N}_{G}(z)+FWL[D_{C}(z)]\hat{D}_{G}(z);
\end{equation}
\item the direct loop product $\frac{FWL[N_{C}(z)]}{FWL[D_{C}(z)]}\cdot \frac{\hat{N}_{G}(z)}{\hat{D}_{G}(z)}$ has no pole-zero cancellation on or outside the unit circle.
\end{itemize}
\end{mylemma}

@@

\begin{proof}
Considering $\nu(k)$ a random process, where $\nu(k)$ is independent from $\nu(k+i)$ for every  integer $k\neq 0$. The autocorrelation function of $\nu(k)$, {\it i.e.} $R_{\nu\nu}(\tau)$ may be computed as follows:
\begin{equation}
R_{\nu\nu}(\tau)=E[\nu(t+\tau)\nu(t)]=\sigma_{Q}^{2}\cdot \delta(\tau),
\end{equation}
where $\delta(\tau)$ is the Dirac delta function at delay time $\tau$.
